---
title: "Capstone Dashboard"
author: "Kendelle Brown, Abby Henderson"
date: "April 14, 2019"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r setup, chunk-1, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(flexdashboard)
library(knitr, quietly=TRUE)
library(dplyr, quietly=TRUE)
library(pander, quietly=TRUE)
library(devtools, quietly=TRUE)
library(censusapi, quietly=TRUE)
library(maptools, quietly=TRUE)
library(rgdal, quietly=TRUE)
library(geojsonio, quietly=TRUE)
library(rmapshaper, quietly=TRUE)
library(sf, quietly=TRUE)
library(ggplot2, quietly=TRUE)
library(tidyr, quietly=TRUE)
library(viridis, quietly=TRUE)
library(gridExtra, quietly=TRUE)
library( leaflet, quietly=TRUE )
library( sp, quietly=TRUE)
library(broom, quietly=TRUE)
library(DT, quietly=TRUE)

Censuskey <- "9cb83c4560f4fbcc326ddd18ea31460fdd34546f"

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)

```

```{r, chunk-2, include=FALSE, cache=FALSE}
# Import Shapefile

download.file( "https://github.com/lecy/neighborhood_change_phx/raw/master/shapefiles/tl_2010_04013_tract10.zip", 
"maricopa-az-census_tract10.zip" )
unzip( "maricopa-az-census_tract10.zip" )
file.remove( "maricopa-az-census_tract10.zip" )
dir()

library( rgdal )
phx <- readOGR("tl_2010_04013_tract10.shp")
head( phx@data, 10)
plot( phx )

phx <- spTransform( phx, CRS("+proj=longlat +datum=WGS84") )

url <- "https://raw.githubusercontent.com/lecy/neighborhood_change_phx/master/data/phx.combined.data.csv"
dat <- read.csv( url, stringsAsFactors=F )


phx$geoid2 <- paste0( "G", phx$STATEFP10, 
                     "0", phx$COUNTYFP10, "0", phx$TRACTCE10 )

phx.shape.data <- merge(phx, dat, by.x="geoid2", by.y="GISJOIN", all.x=T)

phx_fortified <- tidy( phx, region = "geoid2")

phx.tidy <- merge( phx_fortified, dat, by.x="id", by.y="GISJOIN", all.x=T)


asian_1990 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=
Asian_1990)) +
  geom_polygon() +  coord_map() +
     scale_fill_distiller(palette="Paired", direction=1, name="Population") +
     labs(title="Asian Population in 1990", title.cex=.75, caption="1990 Source: US Census, NHGIS")

asian_2000 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, group = group, fill = Asian_2000 ) ) + 
  geom_polygon() + coord_map()+
  scale_fill_distiller(palette="Paired", direction=1, name="Population") +
  labs(title="Asian Population in 2000", caption="2000 Source: NHGIS IPUMS data")


asian_2010 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=
Asian_2010)) +
  geom_polygon() +  coord_map() +
     scale_fill_distiller(palette="Paired", direction=1, name="Population") +
     labs(title="Asian Population in 2010", title.cex=.75, caption="2010 Source: US Census, NHGIS")

asian_2015 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=Asian_2015)) +
  geom_polygon() +  coord_map() +
  scale_fill_distiller(palette="Paired", direction=1, name="Population") +
  labs(title="Asian Population in 2015", caption="2015 Source: US Census")



forsale_1990 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=
Vacant_ForSale_1990)) + geom_polygon() +  coord_map() +
     scale_fill_distiller(palette="Dark2", direction=1, name="Population") +
     labs(title="Vacant For Sale Housing Unit 1990 in Maricopa County", title.cex=.75, caption="1990 Source: US Census, NHGIS")

forsale_2000 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=
Vacant_ForSale_2000)) + geom_polygon() +  coord_map() +
     scale_fill_distiller(palette="RdYlGn", direction=1, name="Population") +
     labs(title="Vacant For Sale Housing Unit 2000 in Maricopa County", title.cex=.75, caption="2000 Source: US Census, NHGIS")

forsale_2010 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=
Vacant_ForSale_2010)) + geom_polygon() +  coord_map() +
     scale_fill_distiller(palette="RdYlGn", direction=1, name="Population") +
     labs(title="Vacant For Sale Housing Unit 2010 in Maricopa County", title.cex=.75, caption="2010 Source: US Census, NHGIS")

forsale_2015 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=
Forsale_2015)) + geom_polygon() +  coord_map() +
  scale_fill_distiller(palette="RdYlGn", direction=1, name="Population") +
  labs(title="For Sale", title.cex=0.5, caption="2015 Source: US Census")

twohundredkto250k_value_2010 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill= 
                      Twohundredkto250k_value_2010)) + geom_polygon() +  coord_map() +
  scale_fill_distiller(palette="BuGn", direction=1, name="Population") +
  labs(title="Between $200,000 and $250,000", title.cex=0.5, caption="2010 Source: US Census")

twohundredkto250k_value_2015 <- ggplot( data = phx.tidy, 
               aes( x = long, y = lat, 
                    group = group, fill=
                      Twohundredkto250k_value_2015)) + geom_polygon() +  coord_map() +
  scale_fill_distiller(palette="BuGn", direction=1, name="Population") +
  labs(title="Between $200,000 and $250,000", title.cex=0.5, caption="2015 Source: US Census")



```

Narrative
=====================================  
    
Column {data-width=600}
-------------------------------------

### Narrative
    
### The narrative will go here


Race {data-orientation=rows}
=====================================     

Inputs {.sidebar data-width=300}
-----------------------------------------------------------------------

```{r, chunk-3, include=TRUE, cache=FALSE}

ui <- fluidPage(
    
  selectInput(inputId= "select", label = h3("Select Year"), 
    choices = list("1990" = 1990, "2000" = 2000, "2010" = 2010, "2015" = 2015), 
    selected = 2000),
  
  hr(),
  fluidRow(column(3, verbatimTextOutput("value")))
  
)

server <- function(input,output)
{

  
  output$value <- renderPrint({ input$select })

}

shinyApp(ui = ui, server=server)
```
   
Row {data-height=400}
-------------------------------------

### Map 1

```{r, chunk-4}
#filler

asian_1990

```

### Map 2

```{r, chunk-5}
#filler

asian_2015


```   

Row {data-height=500}
-------------------------------------  
### Analysis



Ethnicity {data-orientation=rows}
=====================================     

Inputs {.sidebar data-width=300}
-------------------------------------

```{r, chunk-6, cache=FALSE}
# shiny inputs defined here


ui <- fluidPage(

radioButtons(inputId = "radio", label = h3("Select a year"), choices = list("1990" = 1990, "2000" = 2000, "2010" = 2010, "2015" = 2015), selected=2000 ),
  
hr(),
fluidRow(column(3, verbatimTextOutput("value")))
)

server <- function(input, output) { 

  output$value <- renderPrint({input$radio })
  }

shinyApp(ui = ui, server=server)


```
 
Row {data-height=400}
-------------------------------------

### Map 1

```{r, chunk-7}

forsale_2000
```

### Map 2

```{r, chunk-8}

forsale_2010
```   

Row {data-height=500}
-------------------------------------  
### Analysis

```{r, chunk-9}
```

Homes for Sale {data-orientation=rows}
=====================================     
   
Inputs {.sidebar data-width=300}
-------------------------------------

```{r, chunk-10, include=FALSE, cache=FALSE}
# shiny inputs defined here



ui <- fluidPage(

radioButtons(inputId = "radio", label = h3("Select a year"), choices = list("1990" = 1990, "2000" = 2000, "2010" = 2010, "2015" = 2015), selected=2000 ),
  
hr(),
fluidRow(column(3, verbatimTextOutput("value")))
)

server <- function(input, output) { 

  output$value <- renderPrint({input$radio })
}

shinyApp(ui = ui, server=server)
```

```{r, cache=FALSE, include=TRUE}
shinyApp(ui = ui, server=server)
```
 
Row {data-height=400}
-------------------------------------

### Map 1

```{r, chunk-11}

twohundredkto250k_value_2010 

```

### Map 2

```{r, chunk-12}

twohundredkto250k_value_2015

```   

Row {data-height=500}
-------------------------------------  
### Analysis

```{r, chunk-13}
```

Dataset {data-orientation=rows}
=====================================     

### NHGIS 1990,2000,2010 & ACS 2010, 2015

This data table is a sample of the full dataset, including only those variables used in the narratives of this dashboard. For a full dataset, please visit ("link here"). 

```{r, chunk-14, include=FALSE}

dat.selected <- select(dat, GISJOIN, STATE, COUNTY, TRACTA, Asian_1990, Asian_2000, Asian_2010, Asian_2015, HSDiploma_GED_2010, HSdiploma_2015, Twohundredkto250k_value_2010, Twohundredkto250k_value_2015, Male_1990, Female_1990, Male_2000, Female_2000, Male_2010, Female_2010, Male_2015, Female_2015 )
```

```{r, include=FALSE}
these.buttons <- c( 'copy', 'csv', 'excel' )

dat.selected.table <- datatable( dat.selected,
           filter='top', rownames=FALSE, 
           #options=list( pageLength=50, autoWidth=TRUE ),
           fillContainer=TRUE, 
           style="default",
           class='table-condensed table-striped',
           extensions = 'Buttons', 
           options=list( dom='Bfrtip', 
                         buttons=these.buttons  )) %>%
  formatStyle( "GISJOIN", "white-space"="nowrap" )



```

```{r}

selected.datatable

```

Variable Crosswalk {data-orientation=rows}
=====================================     
   

### Data Table Variable Names

This data table includes the names of the different variables from 1990-2015. Notes that 1990, 2000, and 2010 are the variable names from the NHGIS time series data tables downloaded at ("link goes here"). The 2015 variable names are those used to download data from the ACS 5 using the censusapi() package ("link goes here").

```{r, chunk-15, include=FALSE}

url2 <- "https://raw.githubusercontent.com/lecy/neighborhood_change_phx/master/data/phx.variable.name.crosswalk.csv"

phx.var.crosswalk <- read.csv( url2, stringsAsFactors = F)

these.buttons <- c( 'copy', 'csv', 'excel' )

phx.var.datatable <- datatable( phx.var.crosswalk,
           filter='top', rownames=FALSE, 
           #options=list( pageLength=50, autoWidth=TRUE ),
           fillContainer=TRUE, 
           style="default",
           class='table-condensed table-striped',
           extensions = 'Buttons', 
           options=list( dom='Bfrtip', 
                         buttons=these.buttons  )) %>%
  formatStyle( "construct", "white-space"="nowrap" )

```

```{r}
phx.var.datatable
```
