---
title: "Untitled"
author: "Abby Henderson"
date: "4/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
devtools::install_github("hrbrmstr/spdorling")

library(geojsonio)
library(tidyverse)

download.file( "https://github.com/lecy/neighborhood_change_phx/raw/master/shapefiles/tl_2010_04013_tract10.zip", 
"maricopa-az-census_tract10.zip" )
unzip( "maricopa-az-census_tract10.zip" )
file.remove( "maricopa-az-census_tract10.zip" )
dir()

library( rgdal )
phx <- readOGR("tl_2010_04013_tract10.shp")
head( phx@data, 10)
plot( phx )

proj4string( phx )
phx <- spTransform( phx, CRS("+proj=longlat +datum=WGS84") )
proj4string( phx )


```

```{r}

url <- "https://raw.githubusercontent.com/lecy/neighborhood_change_phx/master/data/raw/NHGIS_geog_data.csv"
dat <- read.csv( url, stringsAsFactors=F )

#Create GEOID of FIPS Code elements
phx$geoid <- paste0( "G", phx$STATEFP10, "0", phx$COUNTYFP10, "0", phx$TRACTCE10 )

# > head( phx$geoid )
# [1] "G0400130422644" "G0400130422643" "G0400130422642" "G0400130422641"

phx <- merge( phx, dat, by.x="geoid", by.y="GISJOIN", all.x=T )


```
### create a new directory for your data
dir.create( "shapefiles" )
setwd( "./shapefiles" )

### download TIGER shapefile from GitHub or Census
download.file( "https://github.com/lecy/neighborhood_change_phx/raw/master/shapefiles/tl_2010_04013_tract10.zip", 
"maricopa-az-census_tract10.zip" )
unzip( "maricopa-az-census_tract10.zip" )
file.remove( "maricopa-az-census_tract10.zip" )
dir()


library( rgdal )
phx <- readOGR("tl_2010_04013_tract10.shp")
head( phx@data, 10)

plot( phx )
proj4string( phx )
phx <- spTransform( phx, CRS("+proj=longlat +datum=WGS84") )
proj4string( phx )





set.seed(2010)
phx$val <- sample(10000, 916)

dor <- dorling_from_sp(phx, value=phx$val, quiet=FALSE)


discs_df <- fortify(phx$discs)


url <- "https://raw.githubusercontent.com/lecy/neighborhood_change_phx/master/data/raw/NHGIS_geog_data.csv"
dat <- read.csv( url, stringsAsFactors=F )

#Create GEOID of FIPS Code elements
phx$geoid <- paste0( "G", phx$STATEFP10, "0", phx$COUNTYFP10, "0", phx$TRACTCE10 )

# > head( phx$geoid )
# [1] "G0400130422644" "G0400130422643" "G0400130422642" "G0400130422641"

phx <- merge( phx, dat, by.x="geoid", by.y="GISJOIN", all.x=T )


library(geojsonio)
geojson_write( phx, file = "phx.2010.tracts.geojson" )